---
title: "GP_Evaluation4_3"
author: "Yuanxi Cheng"
date: "2022-09-11"
output: html_document
---
```{r setup6, include=FALSE}
library(usmap)
library(ggplot2)
library(shiny)
library(knitr)


boys <- read.csv("JGSBoys.csv", head= T)
girls <- read.csv("JGSGirls.csv", head=T)
State_Pop <- read.csv("State_Population.csv", head = T)
State_Income <- read.csv("State_Med_Income.csv", head = T)
State_Courses <- read.csv("State_Courses.csv", head = T)
State_Weather <- read.csv("State_Weather.csv", head = T)


#Processing data for JGS boys

boysUS <- boys[(boys$Ctry=="US"),]
boysUS$St.Prov <- toupper(boysUS$St.Prov)
boysUS <- boysUS[!((boysUS$St.Prov=="--"|boysUS$St.Prov=="BC"|boysUS$St.Prov=="AB"|boysUS$St.Prov=="GU"|boysUS$St.Prov=="DC"|boysUS$St.Prov=="PR")),]
boysUS <- subset(boysUS, select = -c(1,2,7,9,10,11,12,13))
rownames(boysUS) <- 1:nrow(boysUS)

#Processing JGS Girls
girlsUS <- girls[(girls$Ctry=="US"),]
girlsUS$St.Prov <- toupper(girlsUS$St.Prov)
girlsUS <- girlsUS[!((girlsUS$St.Prov=="--"|girlsUS$St.Prov=="BC"|girlsUS$St.Prov=="AB"|girlsUS$St.Prov=="GU"|girlsUS$St.Prov=="DC"|girlsUS$St.Prov=="PR")),]
girlsUS <- subset(girlsUS, select = -c(1,2,7,9,10,11,12,13))
rownames(girlsUS) <- 1:nrow(girlsUS)

#boys US map
boys_map <- data.frame(state = unique(boysUS$St.Prov))
boys_map[nrow(boys_map) + 1,] <- c("AK")
Bpopulation <- c()
for (i in boys_map$state) {
  temp_count = 0
  for (k in boysUS$St.Prov) {
    if (i == k) {
      temp_count = temp_count + 1
    }
  }
  Bpopulation <- c(Bpopulation, temp_count)
}
#Bpopulation
boys_map$pop <- Bpopulation
boys_map <- boys_map[order(boys_map$state),]
rownames(boys_map) <- 1:nrow(boys_map)
#head(boys_map, 10)

p1<- plot_usmap(regions = "states", data = boys_map, values = "pop", color = "black")+
   scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
   labs(title = "JGS Boys in US", subtitle = "Population of Competitive Junior Golf Boys across the US") +
   theme(legend.position = "right")

#girls US map
girls_map <- data.frame(state = unique(girlsUS$St.Prov))
girls_map[nrow(girls_map) + 1,] <- c("SD")
girls_map[nrow(girls_map) + 1,] <- c("AK")
girls_map[nrow(girls_map) + 1,] <- c("VT")
girls_map[nrow(girls_map) + 1,] <- c("ME")
Gpopulation <- c()
for (i in girls_map$state) {
  temp_count1 = 0
  for (k in girlsUS$St.Prov) {
    if (i == k) {
      temp_count1 = temp_count1 + 1
    }
  }
  Gpopulation <- c(Gpopulation, temp_count1)
}
girls_map$pop <- Gpopulation
girls_map <- girls_map[order(girls_map$state),]
rownames(girls_map) <- 1:nrow(girls_map)
#head(girls_map, 10)

p2<- plot_usmap(regions = "states", data = girls_map, values = "pop", color = "black")+
   scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
   labs(title = "JGS Girls in US", subtitle = "Population of Competitive Junior Golf Girls across the US") +
   theme(legend.position = "right")

#Combined Map 
boys_temp <- boys_map
girls_temp <- girls_map
for (i in 1:50) {
  boys_temp$pop[i] <- boys_temp$pop[i]+girls_temp$pop[i] 
}
junior_map <- boys_temp
p3<- plot_usmap(regions = "states", data = junior_map, values = "pop", color = "black")+
   scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
   labs(title = "JGS Players in US", subtitle = "Population of Competitive Junior Players Across the US") +
   theme(legend.position = "right")

#Boys With standardized population
State_Pop_Temp <- State_Pop[-c(1:5),]
State_Pop_Temp$NAME <- state.abb[match(State_Pop_Temp$NAME,state.name)]
State_Pop_Temp <- State_Pop_Temp[order(State_Pop_Temp$NAME),]
rownames(State_Pop_Temp) <- 1:nrow(State_Pop_Temp)
pop_stand_boys <- boys_map
for (i in 1:50) {
  pop_stand_boys$pop[i] <- pop_stand_boys$pop[i]/State_Pop_Temp$POPESTIMATE2021[i]
}
p4<- plot_usmap(regions = "states", data = pop_stand_boys, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "JGS Boys in US With Standardized Population", subtitle = "Population of Competitive Junior Golf Boys across the US, 
       standardized by estimate population of people in each state.") +
  theme(legend.position = "right")

#Girls With Standardized Population
pop_stand_girls <- girls_map
for (i in 1:50) {
  pop_stand_girls$pop[i] <- pop_stand_girls$pop[i]/State_Pop_Temp$POPESTIMATE2021[i]
}
p5<- plot_usmap(regions = "states", data = pop_stand_girls, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "JGS Girls in US With Standardized Population", subtitle = "Population of Competitive Junior Golf Girls across the US,
       standardized by estimate population of people in each state.") +
  theme(legend.position = "right")

#Combined With Standardized Population
pop_stand_junior <- junior_map
for (i in 1:50) {
  pop_stand_junior$pop[i] <- pop_stand_junior$pop[i]/State_Pop_Temp$POPESTIMATE2021[i]
}
p6<- plot_usmap(regions = "states", data = pop_stand_junior, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "JGS Players in US With Standardized Population", subtitle = "Population of Competitive Junior Golf Players across the US, 
       standardized by estimate population of people in each state.") +
  theme(legend.position = "right")

    # Quick conversion of State_Courses' state names using State_Income
colnames(State_Income)[1] <- "State"
State_Income <- State_Income[order(State_Income$State),]
State_Courses["State"] <- State_Income["State"]


#Map of Median Household Income by State
#head(State_Income,5)
State_Income$State <- state.abb[match(State_Income$State,state.name)]
State_Income <- State_Income[order(State_Income$State),]
rownames(State_Income) <- 1:nrow(State_Income)
colnames(State_Income)[1] <- "state"

p7<-plot_usmap(regions = "states", data = State_Income, values = "HouseholdIncome", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Income Amount", label = scales::comma)+
  labs(title = "Median Household Income", subtitle = "Census of the median reported household income per state") +
  theme(legend.position = "right")

  #Total Players divided household income
pop_per_income <- junior_map
pop_per_income$pop <- pop_per_income$pop*(State_Income$HouseholdIncome/10000)

p8<-plot_usmap(regions = "states", data = pop_per_income, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Players Per Median Household Income", subtitle = "Players in each state standardized by median income") +
  theme(legend.position = "right")


#Map of golf courses in each state
#head(State_Courses, 5)
State_Courses$State <- state.abb[match(State_Courses$State,state.name)]
colnames(State_Courses)[1] <- "state"
colnames(State_Courses)[2] <- "Courses"
State_Courses$Courses <- as.numeric(State_Courses$Courses)
State_Courses[is.na(State_Courses)] = 1044
p9<-plot_usmap(regions = "states", data = State_Courses, values = "Courses", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Golf Courses", label = scales::comma)+
  labs(title = "Golf Courses By State", subtitle = "Number of established golf courses across each state") +
  theme(legend.position = "right")


#Map of players per golf courses in each state
pop_per_course <- junior_map
for (i in 1:50) {
  pop_per_course$pop[i] <- (pop_per_course$pop[i]*State_Courses$Courses[i])/100000
}
p10<-plot_usmap(regions = "states", data = pop_per_course, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index Num", label = scales::comma)+
  labs(title = "JGS Players in US in Relation to Courses", subtitle = "Population of Competitive Junior Golf Players across the US 
       divided by the total number of golf courses in each state") +
  theme(legend.position = "right")

#For girls only
pop_per_course_girls <- girls_map
for (i in 1:50) {
  pop_per_course_girls$pop[i] <- (pop_per_course_girls$pop[i]*State_Courses$Courses[i])/100000
}
p11<- plot_usmap(regions = "states", data = pop_per_course_girls, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "JGS Girls in US in Relation to Courses", subtitle = "Population of Competitive Junior Golf Girls across the US 
       divided by the total number of golf courses in each state") +
  theme(legend.position = "right")

  #For Boys only
pop_per_course_boys <- boys_map
for (i in 1:50) {
  pop_per_course_boys$pop[i] <- (pop_per_course_boys$pop[i]*State_Courses$Courses[i])/100000
}

p12<-plot_usmap(regions = "states", data = pop_per_course_boys, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "JGS Boys in US in Relation to Courses", subtitle = "Population of Competitive Junior Golf Boys across the US 
       divided by the total number of golf courses in each state") +
  theme(legend.position = "right")

#Map of girls to all juniors ratio
gtotal_ratio <- girls_map
gtotal_ratio$pop <- gtotal_ratio$pop/junior_map$pop
p13<-plot_usmap(regions = "states", data = gtotal_ratio, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "Girls to Player Ratio Per State", subtitle = "ratio of Junior Girls to Junior Players in each state") +
  theme(legend.position = "right")

  #boys
btotal_ratio <- boys_map
btotal_ratio$pop <- btotal_ratio$pop/junior_map$pop
p13_1<-plot_usmap(regions = "states", data = btotal_ratio, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "Boys to Player Ratio Per State", subtitle = "ratio of Junior Boys to Junior Players in each state") +
  theme(legend.position = "right")

#Map of Avg Weather
State_Weather$state <- state.abb[match(State_Weather$state,state.name)]
p14<-plot_usmap(regions = "states", data = State_Weather, values = "AvgF", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Temp", label = scales::comma)+
  labs(title = "Avg Temp by State", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

  #Map of Precipitation
p15<-plot_usmap(regions = "states", data = State_Weather, values = "mm", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "mm", label = scales::comma)+
  labs(title = "Avg Precipitation by State", subtitle = "The annual precipitation from 1971-2000 of each state by millimeters") +
  theme(legend.position = "right")

  #Map of Percent Humidity
p16<-plot_usmap(regions = "states", data = State_Weather, values = "Afternoon", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Percent", label = scales::comma)+
  labs(title = "Annual Avg Relative Humidity by State", subtitle = "The annual percent humidity of each state from 1971-2000") +
  theme(legend.position = "right")

#Player vs Avg Temp
juniorVsTemp <- junior_map
juniorVsTemp$pop <- juniorVsTemp$pop/State_Weather$AvgF
p17<-plot_usmap(regions = "states", data = juniorVsTemp, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Player Population in Relation to Avg Temp", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

#Player vs Avg Precipitation
juniorVsPrecip <- junior_map
juniorVsPrecip$pop <- juniorVsPrecip$pop/State_Weather$mm
p18<-plot_usmap(regions = "states", data = juniorVsPrecip, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Player Population in Relation to Avg Temp", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

#Player vs Afternoon Humidity
juniorVsHum <- junior_map
juniorVsHum$pop <- juniorVsHum$pop/State_Weather$Afternoon
p19<-plot_usmap(regions = "states", data = juniorVsHum, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Player Population in Relation to Avg Temp", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

```

```{r setup6_1, include=FALSE}

#Scatter plot Graphs
#Junior population vs State Populations
juniorVsStatePop<- data.frame(x = State_Pop_Temp$POPESTIMATE2021, y= junior_map$pop)
splot1<-ggplot(juniorVsStatePop,aes(x = x,y = y)) +geom_point(colour='blue') + xlab("State Population") + ylab("Golfer Population") + ggtitle("Junior Population Vs State Population")

#Boys and Girl (separated) population vs State Populations
boysVsStatePop <- data.frame(x = State_Pop_Temp$POPESTIMATE2021, y=boys_map$pop)
girlsVsStatePop <- data.frame(x = State_Pop_Temp$POPESTIMATE2021, y=girls_map$pop)
splot2<-ggplot(boysVsStatePop,aes(x = x,y = y), group = measure, colour = measure) +geom_point(colour='blue') +geom_point(data=girlsVsStatePop,colour='red') + xlab("State Population") + ylab("Golfer Population") + ggtitle("Junior Population Vs State Population (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs Household Income by State
boysVsStateInc <- data.frame(x = State_Income$HouseholdIncome, y=boys_map$pop)
girlsVsStateInc <- data.frame(x = State_Income$HouseholdIncome, y=girls_map$pop)
splot3<-ggplot(boysVsStateInc,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsStateInc,colour='red') + xlab("State Income") + ylab("Golfer Population") + ggtitle("Junior Population Vs Annual Med Household Income Per State (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs Golf Courses
boysVsCourses <- data.frame(x = State_Courses$Courses, y=boys_map$pop)
girlsVsCourses <- data.frame(x = State_Courses$Courses, y=girls_map$pop)
splot4<-ggplot(boysVsCourses,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsCourses,colour='red') + xlab("Golf Courses") + ylab("Golfer Population") + ggtitle("Junior Population Vs Golf Courses Per State (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Temperature 
boysVsTemp <- data.frame(x = State_Weather$AvgF, y=boys_map$pop)
girlsVsTemp <- data.frame(x = State_Weather$AvgF, y=girls_map$pop)
splot5<-ggplot(boysVsTemp,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsTemp,colour='red') + xlab("Avg Temperature Fahrenheit") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Temperature (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Precipitation
boysVsPrecip <- data.frame(x = State_Weather$mm, y=boys_map$pop)
girlsVsPrecip <- data.frame(x = State_Weather$mm, y=girls_map$pop)
splot6<-ggplot(boysVsPrecip,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsPrecip,colour='red') + xlab("Precipitation") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Precipiation (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Humidity in Morning
boysVsMornHum <- data.frame(x = State_Weather$Morning, y=boys_map$pop)
girlsVsMornHum <- data.frame(x = State_Weather$Morning, y=girls_map$pop)
splot7<-ggplot(boysVsMornHum,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsMornHum,colour='red') + xlab("Morning Humidity") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Humidity in AM (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Humidity in Afternoon
boysVsAfterHum <- data.frame(x = State_Weather$Afternoon, y=boys_map$pop)
girlsVsAfterHum <- data.frame(x = State_Weather$Afternoon, y=girls_map$pop)
splot8<-ggplot(boysVsAfterHum,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsAfterHum,colour='red') + xlab("Afternoon Humidity (%)") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Humidity in PM (Boys = Blue, Girls = Red)")

#fitting linear models
#boys & girls pop vs state pop
boysVsStatePopLm <- lm(y ~ x, data = boysVsStatePop)
girlsVsStatePopLm <- lm(y ~ x, data = girlsVsStatePop)
#boys & girls pop vs state income
boysVsStateIncLm <- lm(y ~ x, data = boysVsStateInc)
girlsVsStateIncLm <- lm(y ~ x, data = girlsVsStateInc)
#boys & girls pop vs state courses
boysVsCoursesLm <- lm(y ~ x, data = boysVsCourses)
girlsVsCoursesLm <- lm(y ~ x, data = girlsVsCourses)
#boys & girls pop vs state average temp
boysVsTempLm <- lm(y ~ x, data = boysVsTemp)
girlsVsTempLm <- lm(y ~ x, data = girlsVsTemp)
#boys & girls pop vs state precipitation
boysVsPrecipLm <- lm(y ~ x, data = boysVsPrecip)
girlsVsPrecipLm <- lm(y ~ x, data = girlsVsPrecip)
#boys & girls pop vs state humidity AM
boysVsMornHumLm <- lm(y ~ x, data = boysVsMornHum)
girlsVsMornHumLm <- lm(y ~ x, data = girlsVsMornHum)
#boys & girls pop vs state humidity PM
boysVsAfterHumLm <- lm(y ~ x, data = boysVsAfterHum)
girlsVsAfterHumLm <- lm(y ~ x, data = girlsVsAfterHum)

#visualizing linear models
par(mfrow=c(2,2))

summary(boysVsStatePopLm)
plot(boysVsStatePopLm)

summary(girlsVsStatePopLm)
plot(girlsVsStatePopLm)

summary(boysVsStateIncLm)
plot(boysVsStateIncLm)

summary(girlsVsStateIncLm)
plot(girlsVsStateIncLm)

summary(boysVsCoursesLm)
plot(boysVsCoursesLm)

summary(girlsVsCoursesLm)
plot(girlsVsCoursesLm)

summary(boysVsTempLm)
plot(boysVsTempLm)

summary(girlsVsTempLm)
plot(girlsVsTempLm)

summary(boysVsPrecipLm)
plot(boysVsPrecipLm)

summary(girlsVsPrecipLm)
plot(girlsVsPrecipLm)

summary(boysVsMornHumLm)
plot(boysVsMornHumLm)

summary(girlsVsMornHumLm)
plot(girlsVsMornHumLm)

summary(boysVsAfterHumLm)
plot(boysVsAfterHumLm)

summary(girlsVsAfterHumLm)
plot(girlsVsAfterHumLm)

par(mfrow=c(1,1))

```

## Evaluation of Total Player Population Vs Average Annual Humidity in the Afternoon


### Map of Average Humidity in percent

```{r weatherHum, echo=FALSE}
print(p16)
print(p19)
```


#### There isn't really a noticable relationship just by observing maps. We could argue that temperature doesn't make a significant affect in where people chose to play golf. There is a heavy concentration of population in California, Texas, and Florida, even after being standardized by temperature. 


## Scatter Plots
```{r splot6, echo=FALSE}
print(splot8)
```

### Fitting Linear Models (Not Standardized Population)

### Boys:

#### Linear Regression Line

```{r lm11, echo=FALSE}
plot(y ~ x, data = boysVsAfterHum, ylab = "Golfer Population", xlab = "Humidity PM (%)")
  abline(boysVsAfterHumLm)
```


#### Analyzing Residuals and Testing Regression:

```{r lm11_1, echo=FALSE}
print(summary(boysVsAfterHumLm))
plot(boysVsAfterHumLm)
```

### Girls:

#### Linear Regression Line

```{r lm12, echo=FALSE}
plot(y ~ x, data = girlsVsAfterHum, ylab = "Golfer Population", xlab = "Humidity PM (%)")
  abline(girlsVsAfterHumLm)
```

#### Analyzing Residuals and Testing Regression:

```{r lm12_1, echo=FALSE}
print(summary(girlsVsAfterHumLm))
plot(girlsVsAfterHumLm)
```


### Linear Modeling Results - Negative

#### The lm() function in R creates a regression model with the given data, and the summary functions reviews the weights and performance measures of the model. The residuals allows us to measure and analyze the difference between prediction and actual results of the linear model. In this project, residuals, along with the p-value, are observed and tested to see how well the single-variable linear regression model fits the data.

#### Weather is another factor that logically seems like a big factor to the popularity of golf. Humidity should be a factor of golf popularity, as it often affects the conditions of golf courses, which int turn may affect the incentives for people to play golf or not. Looking at the scatterplot shows that the data is heavily skewed left, with higher population concentrations in the 50 to 65 percent range. The p value of the linear regression model is above 0.05, so therefore humidity is not a linear predictor of golf popularity.

#### Humidity is ultimately not a significant factor of golf population, at least in a linear apparatus. The truth is that weather shouldn't logically be a linear relationship with golfer population, and it goes to show the limits of linear modeling. The reality is that many scenarios and factors are much more complicated than linear relationships, which is a good thing to understand. 


