---
title: "GP_Evaluation2"
author: "Yuanxi Cheng"
date: "2022-09-09"
output: html_document
---



```{r setup2, include=FALSE}
library(usmap)
library(ggplot2)
library(shiny)
library(knitr)



boys <- read.csv("JGSBoys.csv", head= T)
girls <- read.csv("JGSGirls.csv", head=T)
State_Pop <- read.csv("State_Population.csv", head = T)
State_Income <- read.csv("State_Med_Income.csv", head = T)
State_Courses <- read.csv("State_Courses.csv", head = T)
State_Weather <- read.csv("State_Weather.csv", head = T)


#Processing data for JGS boys

boysUS <- boys[(boys$Ctry=="US"),]
boysUS$St.Prov <- toupper(boysUS$St.Prov)
boysUS <- boysUS[!((boysUS$St.Prov=="--"|boysUS$St.Prov=="BC"|boysUS$St.Prov=="AB"|boysUS$St.Prov=="GU"|boysUS$St.Prov=="DC"|boysUS$St.Prov=="PR")),]
boysUS <- subset(boysUS, select = -c(1,2,7,9,10,11,12,13))
rownames(boysUS) <- 1:nrow(boysUS)

#Processing JGS Girls
girlsUS <- girls[(girls$Ctry=="US"),]
girlsUS$St.Prov <- toupper(girlsUS$St.Prov)
girlsUS <- girlsUS[!((girlsUS$St.Prov=="--"|girlsUS$St.Prov=="BC"|girlsUS$St.Prov=="AB"|girlsUS$St.Prov=="GU"|girlsUS$St.Prov=="DC"|girlsUS$St.Prov=="PR")),]
girlsUS <- subset(girlsUS, select = -c(1,2,7,9,10,11,12,13))
rownames(girlsUS) <- 1:nrow(girlsUS)

#boys US map
boys_map <- data.frame(state = unique(boysUS$St.Prov))
boys_map[nrow(boys_map) + 1,] <- c("AK")
Bpopulation <- c()
for (i in boys_map$state) {
  temp_count = 0
  for (k in boysUS$St.Prov) {
    if (i == k) {
      temp_count = temp_count + 1
    }
  }
  Bpopulation <- c(Bpopulation, temp_count)
}
#Bpopulation
boys_map$pop <- Bpopulation
boys_map <- boys_map[order(boys_map$state),]
rownames(boys_map) <- 1:nrow(boys_map)
#head(boys_map, 10)

p1<- plot_usmap(regions = "states", data = boys_map, values = "pop", color = "black")+
   scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
   labs(title = "JGS Boys in US", subtitle = "Population of Competitive Junior Golf Boys across the US") +
   theme(legend.position = "right")

#girls US map
girls_map <- data.frame(state = unique(girlsUS$St.Prov))
girls_map[nrow(girls_map) + 1,] <- c("SD")
girls_map[nrow(girls_map) + 1,] <- c("AK")
girls_map[nrow(girls_map) + 1,] <- c("VT")
girls_map[nrow(girls_map) + 1,] <- c("ME")
Gpopulation <- c()
for (i in girls_map$state) {
  temp_count1 = 0
  for (k in girlsUS$St.Prov) {
    if (i == k) {
      temp_count1 = temp_count1 + 1
    }
  }
  Gpopulation <- c(Gpopulation, temp_count1)
}
girls_map$pop <- Gpopulation
girls_map <- girls_map[order(girls_map$state),]
rownames(girls_map) <- 1:nrow(girls_map)
#head(girls_map, 10)

p2<- plot_usmap(regions = "states", data = girls_map, values = "pop", color = "black")+
   scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
   labs(title = "JGS Girls in US", subtitle = "Population of Competitive Junior Golf Girls across the US") +
   theme(legend.position = "right")

#Combined Map 
boys_temp <- boys_map
girls_temp <- girls_map
for (i in 1:50) {
  boys_temp$pop[i] <- boys_temp$pop[i]+girls_temp$pop[i] 
}
junior_map <- boys_temp
p3<- plot_usmap(regions = "states", data = junior_map, values = "pop", color = "black")+
   scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
   labs(title = "JGS Players in US", subtitle = "Population of Competitive Junior Players Across the US") +
   theme(legend.position = "right")

#Boys With standardized population
State_Pop_Temp <- State_Pop[-c(1:5),]
State_Pop_Temp$NAME <- state.abb[match(State_Pop_Temp$NAME,state.name)]
State_Pop_Temp <- State_Pop_Temp[order(State_Pop_Temp$NAME),]
rownames(State_Pop_Temp) <- 1:nrow(State_Pop_Temp)
pop_stand_boys <- boys_map
for (i in 1:50) {
  pop_stand_boys$pop[i] <- pop_stand_boys$pop[i]/State_Pop_Temp$POPESTIMATE2021[i]
}
p4<- plot_usmap(regions = "states", data = pop_stand_boys, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "JGS Boys in US With Standardized Population", subtitle = "Population of Competitive Junior Golf Boys across the US, 
       standardized by estimate population of people in each state.") +
  theme(legend.position = "right")

#Girls With Standardized Population
pop_stand_girls <- girls_map
for (i in 1:50) {
  pop_stand_girls$pop[i] <- pop_stand_girls$pop[i]/State_Pop_Temp$POPESTIMATE2021[i]
}
p5<- plot_usmap(regions = "states", data = pop_stand_girls, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "JGS Girls in US With Standardized Population", subtitle = "Population of Competitive Junior Golf Girls across the US,
       standardized by estimate population of people in each state.") +
  theme(legend.position = "right")

#Combined With Standardized Population
pop_stand_junior <- junior_map
for (i in 1:50) {
  pop_stand_junior$pop[i] <- pop_stand_junior$pop[i]/State_Pop_Temp$POPESTIMATE2021[i]
}
p6<- plot_usmap(regions = "states", data = pop_stand_junior, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "JGS Players in US With Standardized Population", subtitle = "Population of Competitive Junior Golf Players across the US, 
       standardized by estimate population of people in each state.") +
  theme(legend.position = "right")

    # Quick conversion of State_Courses' state names using State_Income
colnames(State_Income)[1] <- "State"
State_Income <- State_Income[order(State_Income$State),]
State_Courses["State"] <- State_Income["State"]


#Map of Median Household Income by State
#head(State_Income,5)
State_Income$State <- state.abb[match(State_Income$State,state.name)]
State_Income <- State_Income[order(State_Income$State),]
rownames(State_Income) <- 1:nrow(State_Income)
colnames(State_Income)[1] <- "state"

p7<-plot_usmap(regions = "states", data = State_Income, values = "HouseholdIncome", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Income Amount", label = scales::comma)+
  labs(title = "Median Household Income", subtitle = "Census of the median reported household income per state") +
  theme(legend.position = "right")

  #Total Players divided household income
pop_per_income <- junior_map
pop_per_income$pop <- pop_per_income$pop*(State_Income$HouseholdIncome/10000)

p8<-plot_usmap(regions = "states", data = pop_per_income, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Players Per Median Household Income", subtitle = "Players in each state standardized by median income") +
  theme(legend.position = "right")


#Map of golf courses in each state
#head(State_Courses, 5)
State_Courses$State <- state.abb[match(State_Courses$State,state.name)]
colnames(State_Courses)[1] <- "state"
colnames(State_Courses)[2] <- "Courses"
State_Courses$Courses <- as.numeric(State_Courses$Courses)
State_Courses[is.na(State_Courses)] = 1044
p9<-plot_usmap(regions = "states", data = State_Courses, values = "Courses", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Golf Courses", label = scales::comma)+
  labs(title = "Golf Courses By State", subtitle = "Number of established golf courses across each state") +
  theme(legend.position = "right")


#Map of players per golf courses in each state
pop_per_course <- junior_map
for (i in 1:50) {
  pop_per_course$pop[i] <- (pop_per_course$pop[i]*State_Courses$Courses[i])/100000
}
p10<-plot_usmap(regions = "states", data = pop_per_course, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index Num", label = scales::comma)+
  labs(title = "JGS Players in US in Relation to Courses", subtitle = "Population of Competitive Junior Golf Players across the US 
       divided by the total number of golf courses in each state") +
  theme(legend.position = "right")

#For girls only
pop_per_course_girls <- girls_map
for (i in 1:50) {
  pop_per_course_girls$pop[i] <- (pop_per_course_girls$pop[i]*State_Courses$Courses[i])/100000
}
p11<- plot_usmap(regions = "states", data = pop_per_course_girls, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "JGS Girls in US in Relation to Courses", subtitle = "Population of Competitive Junior Golf Girls across the US 
       divided by the total number of golf courses in each state") +
  theme(legend.position = "right")

  #For Boys only
pop_per_course_boys <- boys_map
for (i in 1:50) {
  pop_per_course_boys$pop[i] <- (pop_per_course_boys$pop[i]*State_Courses$Courses[i])/100000
}

p12<-plot_usmap(regions = "states", data = pop_per_course_boys, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "JGS Boys in US in Relation to Courses", subtitle = "Population of Competitive Junior Golf Boys across the US 
       divided by the total number of golf courses in each state") +
  theme(legend.position = "right")

#Map of girls to all juniors ratio
gtotal_ratio <- girls_map
gtotal_ratio$pop <- gtotal_ratio$pop/junior_map$pop
p13<-plot_usmap(regions = "states", data = gtotal_ratio, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "Girls to Player Ratio Per State", subtitle = "ratio of Junior Girls to Junior Players in each state") +
  theme(legend.position = "right")

  #boys
btotal_ratio <- boys_map
btotal_ratio$pop <- btotal_ratio$pop/junior_map$pop
p13_1<-plot_usmap(regions = "states", data = btotal_ratio, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Population Num", label = scales::comma)+
  labs(title = "Boys to Player Ratio Per State", subtitle = "ratio of Junior Boys to Junior Players in each state") +
  theme(legend.position = "right")

#Map of Avg Weather
State_Weather$state <- state.abb[match(State_Weather$state,state.name)]
p14<-plot_usmap(regions = "states", data = State_Weather, values = "AvgF", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Temp", label = scales::comma)+
  labs(title = "Avg Temp by State", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

  #Map of Precipitation
p15<-plot_usmap(regions = "states", data = State_Weather, values = "mm", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "mm", label = scales::comma)+
  labs(title = "Avg Precipitation by State", subtitle = "The annual precipitation from 1971-2000 of each state by millimeters") +
  theme(legend.position = "right")

  #Map of Percent Humidity
p16<-plot_usmap(regions = "states", data = State_Weather, values = "Afternoon", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Percent", label = scales::comma)+
  labs(title = "Annual Avg Relative Humidity by State", subtitle = "The annual percent humidity of each state from 1971-2000") +
  theme(legend.position = "right")

#Player vs Avg Temp
juniorVsTemp <- junior_map
juniorVsTemp$pop <- juniorVsTemp$pop*State_Weather$AvgF/1000
p17<-plot_usmap(regions = "states", data = juniorVsTemp, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Player Population in Relation to Avg Temp", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

#Player vs Avg Precipitation
juniorVsPrecip <- junior_map
juniorVsPrecip$pop <- juniorVsPrecip$pop*State_Weather$mm/1000
p18<-plot_usmap(regions = "states", data = juniorVsPrecip, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Player Population in Relation to Avg Temp", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

#Player vs Afternoon Humidity
juniorVsHum <- junior_map
juniorVsHum$pop <- juniorVsHum$pop*State_Weather$Afternoon/1000
p19<-plot_usmap(regions = "states", data = juniorVsHum, values = "pop", color = "black")+
  scale_fill_continuous(low = "white", high = "red", name = "Index", label = scales::comma)+
  labs(title = "Player Population in Relation to Avg Temp", subtitle = "The annual average temperature from 1971-2000 of each state by Fahrenheit") +
  theme(legend.position = "right")

```

```{r setup2_1, include=FALSE}

#Scatter plot Graphs
#Junior population vs State Populations
juniorVsStatePop<- data.frame(x = State_Pop_Temp$POPESTIMATE2021, y= junior_map$pop)
splot1<-ggplot(juniorVsStatePop,aes(x = x,y = y)) +geom_point(colour='blue') + xlab("State Population") + ylab("Golfer Population") + ggtitle("Junior Population Vs State Population")

#Boys and Girl (separated) population vs State Populations
boysVsStatePop <- data.frame(x = State_Pop_Temp$POPESTIMATE2021, y=boys_map$pop)
girlsVsStatePop <- data.frame(x = State_Pop_Temp$POPESTIMATE2021, y=girls_map$pop)
splot2<-ggplot(boysVsStatePop,aes(x = x,y = y), group = measure, colour = measure) +geom_point(colour='blue') +geom_point(data=girlsVsStatePop,colour='red') + xlab("State Population") + ylab("Golfer Population") + ggtitle("Junior Population Vs State Population (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs Household Income by State
boysVsStateInc <- data.frame(x = State_Income$HouseholdIncome, y=boys_map$pop)
girlsVsStateInc <- data.frame(x = State_Income$HouseholdIncome, y=girls_map$pop)
splot3<-ggplot(boysVsStateInc,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsStateInc,colour='red') + xlab("State Income") + ylab("Golfer Population") + ggtitle("Junior Population Vs Annual Med Household Income Per State (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs Golf Courses
boysVsCourses <- data.frame(x = State_Courses$Courses, y=boys_map$pop)
girlsVsCourses <- data.frame(x = State_Courses$Courses, y=girls_map$pop)
splot4<-ggplot(boysVsCourses,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsCourses,colour='red') + xlab("Golf Courses") + ylab("Golfer Population") + ggtitle("Junior Population Vs Golf Courses Per State (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Temperature 
boysVsTemp <- data.frame(x = State_Weather$AvgF, y=boys_map$pop)
girlsVsTemp <- data.frame(x = State_Weather$AvgF, y=girls_map$pop)
splot5<-ggplot(boysVsTemp,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsTemp,colour='red') + xlab("Avg Temperature Fahrenheit") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Temperature (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Precipitation
boysVsPrecip <- data.frame(x = State_Weather$mm, y=boys_map$pop)
girlsVsPrecip <- data.frame(x = State_Weather$mm, y=girls_map$pop)
splot6<-ggplot(boysVsPrecip,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsPrecip,colour='red') + xlab("Precipitation") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Precipiation (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Humidity in Morning
boysVsMornHum <- data.frame(x = State_Weather$Morning, y=boys_map$pop)
girlsVsMornHum <- data.frame(x = State_Weather$Morning, y=girls_map$pop)
splot7<-ggplot(boysVsMornHum,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsMornHum,colour='red') + xlab("Morning Humidity") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Humidity in AM (Boys = Blue, Girls = Red)")

#boys and Girl (separated) pop vs State Humidity in Afternoon
boysVsAfterHum <- data.frame(x = State_Weather$Afternoon, y=boys_map$pop)
girlsVsAfterHum <- data.frame(x = State_Weather$Afternoon, y=girls_map$pop)
splot8<-ggplot(boysVsAfterHum,aes(x = x,y = y)) +geom_point(colour='blue') +geom_point(data=girlsVsAfterHum,colour='red') + xlab("Afternoon Humidity") + ylab("Golfer Population") + ggtitle("Junior Population Vs Avg Annual Humidity in PM (Boys = Blue, Girls = Red)")

#fitting linear models
#boys & girls pop vs state pop
boysVsStatePopLm <- lm(y ~ x, data = boysVsStatePop)
girlsVsStatePopLm <- lm(y ~ x, data = girlsVsStatePop)
#boys & girls pop vs state income
boysVsStateIncLm <- lm(y ~ x, data = boysVsStateInc)
girlsVsStateIncLm <- lm(y ~ x, data = girlsVsStateInc)
#boys & girls pop vs state courses
boysVsCoursesLm <- lm(y ~ x, data = boysVsCourses)
girlsVsCoursesLm <- lm(y ~ x, data = girlsVsCourses)
#boys & girls pop vs state average temp
boysVsTempLm <- lm(y ~ x, data = boysVsTemp)
girlsVsTempLm <- lm(y ~ x, data = girlsVsTemp)
#boys & girls pop vs state precipitation
boysVsPrecipLm <- lm(y ~ x, data = boysVsPrecip)
girlsVsPrecipLm <- lm(y ~ x, data = girlsVsPrecip)
#boys & girls pop vs state humidity AM
boysVsMornHumLm <- lm(y ~ x, data = boysVsMornHum)
girlsVsMornHumLm <- lm(y ~ x, data = girlsVsMornHum)
#boys & girls pop vs state humidity PM
boysVsAfterHumLm <- lm(y ~ x, data = boysVsAfterHum)
girlsVsAfterHumLm <- lm(y ~ x, data = girlsVsAfterHum)

#visualizing linear models
par(mfrow=c(2,2))

summary(boysVsStatePopLm)
plot(boysVsStatePopLm)

summary(girlsVsStatePopLm)
plot(girlsVsStatePopLm)

summary(boysVsStateIncLm)
plot(boysVsStateIncLm)

summary(girlsVsStateIncLm)
plot(girlsVsStateIncLm)

summary(boysVsCoursesLm)
plot(boysVsCoursesLm)

summary(girlsVsCoursesLm)
plot(girlsVsCoursesLm)

summary(boysVsTempLm)
plot(boysVsTempLm)

summary(girlsVsTempLm)
plot(girlsVsTempLm)

summary(boysVsPrecipLm)
plot(boysVsPrecipLm)

summary(girlsVsPrecipLm)
plot(girlsVsPrecipLm)

summary(boysVsMornHumLm)
plot(boysVsMornHumLm)

summary(girlsVsMornHumLm)
plot(girlsVsMornHumLm)

summary(boysVsAfterHumLm)
plot(boysVsAfterHumLm)

summary(girlsVsAfterHumLm)
plot(girlsVsAfterHumLm)

par(mfrow=c(1,1))

```

## Evaluation of Player Population Vs Annual Median Household Income


### Map of Household Income

```{r stateInc, echo=FALSE}
print(p7)
print(p3)
print(p8)
```


#### When observing and comparing these graphs, it's hard to see any relationship or pattern to the distribution of median income level and popularity of golf. However, it looks like the map of players across the US and players standardized by household income look very similar, giving the notion that there is a possible connection between income and junior players.


## Scatter Plots
```{r splot2, echo=FALSE}
print(splot3)
```

### Fitting Linear Models (Not Standardized Population)

### Boys:

#### Linear Regression Line

```{r lm3, echo=FALSE}
plot(y ~ x, data = boysVsStateInc, ylab = "Golfer Population", xlab = "State Med Income")
  abline(boysVsStateIncLm)
```


#### Analyzing Residuals and Testing Regression:

```{r lm3_1, echo=FALSE}
print(summary(boysVsStateIncLm))
plot(boysVsStateIncLm)
```

### Girls:

#### Linear Regression Line

```{r lm4, echo=FALSE}
plot(y ~ x, data = girlsVsStateInc, ylab = "Golfer Population", xlab = "State Med Income")
  abline(girlsVsStateIncLm)
```

#### Analyzing Residuals and Testing Regression:

```{r lm4_1, echo=FALSE}
print(summary(girlsVsStateIncLm))
plot(girlsVsStateIncLm)
```


### Linear Modeling Results - Negative

#### The lm() function in R creates a regression model with the given data, and the summary functions reviews the weights and performance measures of the model. The residuals allows us to measure and analyze the difference between prediction and actual results of the linear model. Residuals, along with other factors such as the p-value, are observed and tested to see how well the single-variable linear regression model fits the data.

#### In the case of Average Annual Household Income, it does not look like it is a significant predictor in golfer population. Just by looking at the scattor plot, you can see that there isn't really any linear correlation to the points. When fitting the model, the summary function returned a p value of over 0.05, signifying that changes in the predictor (household income) does not associate with changes in the response (golfer population). However, it is important to note that this is all through the scope of a single variable linear regression model.

#### Overall, we can confirm based on our level of analyzation that a linear regression model does not fit Household Income to Golfer Population. Therefore, it is likely that Golfer Population is not a good/significant factor of golf popularity. However, it could still be possible that a polynomial, exponential, or other regression model might be a better fit for this factor. 

